---
title: "Introduction of Minimization Randomization"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction of Minimization Randomization}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
bibliography: reference.bib
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, message = FALSE}
devtools::load_all()
library(dplyr)
library(table1)
```

In this article, we illustrate how to simulate treatment group using minimization randomization.
An introduction of minimiazation randomization can be found in 
<https://online.stat.psu.edu/stat509/lesson/8/8.5> or @pocock1975sequential. 
The implementation is following section 2.2 of @jin2019algorithms. 

> The original paper implemented the algorithm in
> [`Minirand`](https://cran.r-project.org/web/packages/Minirand/index.html)
> Here we provide a pipe friendly and potentially efficient implementation

The current implementation allow

- multiple treatment groups. 
- flexible allocation ratio.
- user specified imbalance function. 
- user specified weight of imbalance. 

To apply minimization randomization, user needs to determine some parameters. 

- sample size: `n`

```{r}
n <- 100
```

- stratum: here we created a function `define_stratum` that uses a named vector 
to specify the category of each stratum and the randomization weight. 

Below is an example of stratum using `sex` with equal weight. 

```{r}
stratum <- define_stratum(sex = c("Male" = 1, "Female" = 1))
stratum
```

Then we can use `simu_stratum` to simulate a data with the pre-defined stratum. 

```{r}
set.seed(1234)
simu_stratum(4, stratum = stratum)
```

- treatment group: 2 group

```{r}
treatment <- c("case", "control")
```

- randomization ratio (default): 1:1
- allocation probability (default): 0.9, 0.1
- stratum weight (default): equal
- imbalance function (default): range (`imbalance_fun_range()`)  

After we specify those parameters, we can use `simu_treatment_minimization()` to 
simulate treatment group using minimization randomization. 

```{r}
set.seed(1234)
df <- n %>% 
  simu_stratum(stratum = stratum) %>% 
  simu_treatment_minimization(treatment = treatment, 
                              ratio = c(1, 1))

head(df)
```

We can check the balance of the sex variable. 

```{r}
table(df$sex)
```
In this toy example, there are only two stratums. 
Using block randomization is more proper in practice. 
The block randomization is implemented in `simu_treatment_block()`. 

```{r}
set.seed(1234)
df <- n %>% 
  simu_stratum(stratum = stratum) %>% 
  simu_treatment_block(treatment = treatment, 
                       ratio = c(1, 1))

head(df)
```

```{r}
table(df$sex)
```

